\newpage
\pagestyle{plain}

\chapter*{Ашигласан ном зохиол}
\addcontentsline{toc}{chapter}{Ашигласан ном зохиол}

\begin{enumerate}

% --- Flutter ба Dart ---
\item Google LLC. (2024). \textit{Flutter Documentation}. https://docs.flutter.dev/

\item Google LLC. (2024). \textit{Dart Programming Language}. https://dart.dev/

\item Windmill, E. (2020). \textit{Flutter in Action}. Manning Publications.

\item Napoli, M. L. (2022). \textit{Beginning Flutter: A Hands-On Guide to App Development}. Wiley.

\item Payne, R. (2021). \textit{Beginning App Development with Flutter: Create Cross-Platform Mobile Apps}. Apress.

% --- Firebase ---
\item Google LLC. (2024). \textit{Firebase Documentation}. https://firebase.google.com/docs

\item Moroney, L. (2017). \textit{The Definitive Guide to Firebase}. Apress.

% --- State Management ---
\item Rousselet, R. (2024). \textit{Provider Package Documentation}. https://pub.dev/packages/provider

% --- Мобайл боловсрол ---
\item Ally, M. (2009). \textit{Mobile Learning: Transforming the Delivery of Education and Training}. AU Press.

\item Crompton, H. (2013). A Historical Overview of M-Learning. \textit{Handbook of Mobile Learning}, 3--14.

\item Deterding, S., Dixon, D., Khaled, R., \& Nacke, L. (2011). From Game Design Elements to Gamefulness: Defining ``Gamification.'' \textit{Proceedings of the 15th International Academic MindTrek Conference}, 9--15.

% --- Програм хангамжийн инженерчлэл ---
\item Pressman, R. S. \& Maxim, B. R. (2019). \textit{Software Engineering: A Practitioner's Approach} (9th ed.). McGraw-Hill Education.

\item Sommerville, I. (2015). \textit{Software Engineering} (10th ed.). Pearson.

\item Beck, K., et al. (2001). \textit{Manifesto for Agile Software Development}. https://agilemanifesto.org/

% --- SQLite ---
\item SQLite Consortium. (2024). \textit{SQLite Documentation}. https://www.sqlite.org/docs.html

% --- UML ---
\item Fowler, M. (2003). \textit{UML Distilled: A Brief Guide to the Standard Object Modeling Language} (3rd ed.). Addison-Wesley.

% --- Монголын түүх ---
\item Weatherford, J. (2004). \textit{Genghis Khan and the Making of the Modern World}. Crown Publishers.

\item May, T. (2012). \textit{The Mongol Conquests in World History}. Reaktion Books.

\item Ratchnevsky, P. (1991). \textit{Genghis Khan: His Life and Legacy}. Blackwell Publishers.

\item Эрдэнэбат, Б. (2010). \textit{Монголын нууц товчоо: Судалгааны бүтээл}. Улаанбаатар.

\item Encyclopaedia Britannica. (2024). \textit{Mongol Empire}. https://www.britannica.com/place/Mongol-empire

% --- Газрын зураг ба визуалчлал ---
\item flutter\_earth\_globe package. (2024). \textit{3D Earth Globe for Flutter}. https://pub.dev/packages/flutter\_earth\_globe

% --- UI/UX дизайн ---
\item Norman, D. (2013). \textit{The Design of Everyday Things} (Revised ed.). Basic Books.

\item Google LLC. (2024). \textit{Material Design Guidelines}. https://m3.material.io/

\end{enumerate}
